---
title: "Lesson 2"
author: "jane"
date: "2020/7/7"
output: html_document
---
```{r}
as.character(5/6)
as.numeric(5/6)
5/6 == as.numeric(as.character(5/6))
print(5/6,digit=10)
```
digit only works with numeric

xaringan
```{r}
pi
0.45-3*0.15
```
Rounding errors tend to accumulate in long calculations.
```{r}
(0.5-0.3)==(0.3-0.1)
all.equal(0.5-0.3,0.3-0.1)
```
FOr statistics, the precision is not in the first ptiority.

# DATA Structure
# Vector:
vector is a sequence of values, __all of the same type__
```{r}
s<-c(1,2,3,4,"as","2","x")
is.vector(s)
s
s[1]
s[4]
s[-3]
m<-vector(length=5);m#empty vector
m[5]<-5;m
#essence of R
x<-c(1,2,3)
y<-c(2,3,4)
x+y
```

## RECTCLING
```{r}
#calculation
x<-c(1,2,3,4)
x+c(4,5)
x ^ c(0,1)
2*x

#Comparision
(x>3) & (x<6)
identical(c(0.5-0.3,0.3-0.1),c(0.3-0.1),(0.5-0.3))
all.equal(c(0.5-0.3,0.3-0.1),c(0.3-0.1,0.5-0.3))
```
## Adressing
```{r}
x[c(2,3)]
x[c(-1,-2)]#use index
x[x>2]
y<--x;y
y[x<2]
a<-vector(length=10)
x[a]
x[!a]# when the length of the boolean differs from x, then will recycle
places<-which(x>2)
places
```

## Named Components
```{r}
names(x)<-c("v1","v2","fred");x
which(names(x)=="fred")
```
```{r}
date()
```

## Function on vectors
```{r}
any()
all()
```

# Array
```{r}
x<-c(7,8,10,45)
x.arr<-array(x,dim=c(2,2));x.arr
x<-c(x,7,8)
x.arr<-array(x,dim=c(2,2,2));x.arr#high dimension!
```
```{r}
is.vector(x.arr)
str(x.arr)
attributes(x.arr)# the attributes of obkect
rowSums(x.arr)
```
_.csv is a kind of plain text that separated by comma_

_coefficients(lm(Median~.))_ REmain to be explored

_complete.cases(data)_ return a vector of nrows, if the row of data have NAN or nNA, then return FALSE
__ggplot2__
usually when it comes to regression, plotting the observed values and fitted values, we usually add _geom_abline()_ to see whether the regression model fits well enough.

P.s The incomes' data follow right long tail distribution

# Mathematical Programming
# Matrix--colomns  of same types
```{r}
factory<-matrix(c(1,2,3,4),ncol=2);factory
factory2<-matrix(c(1,2,3,4),ncol=2,byrow=TRUE);factory2
six.sevens<-matrix(rep(7,6),ncol=3);six.sevens
factory%*%six.sevens
```
## matrices and vectors
```{r}
output <- c(10,20)
factory %*% output
output %*% factory
```

```{r}
t(factory)
det(factory)
diag(factory)
diag(c(1,2))
diag(4)
```
## Inverting
```{r}
factory^-1
solve(factory)# truely invert, solve a linear system factory*factory's invert = E
solve(factory,diag(2))
```
### Why's it called "solve"" anyway?

Solving the linear system $\mathbf{A}\vec{x} = \vec{b}$ for $\vec{x}$:

```{r}
available <- c(1600,70)
solve(factory,available)
factory %*% solve(factory,available)
```

### Names in matrices
rownames()
colnames()

### apply
apply(data,1/2,func)

### List
not all the samw tyoe
```{r}
my_list<-list("happy",7,TRUE);my_list

```
my_list[]:sub list, still list,cannot calculate
my_list[[]]:the elements
### chop off
### Naming
```{r}
names(my_list)<-c("a","b","c")
my_list[1]
my_list[[1]]
```
### Use $ to chooose variables
```{r}
my.distribution[["family"]]
my.distribution$family
```

### Names in lists
```{r}
my_distribution<-list(family="gaussian",mean=7,sd=1,isSymmetric=TRUE)
my_distribution$add<-"y";my_distribution
my_distribution$add<-NULL;my_distribution
```
### Key-Value pairs

# Dataframes
no matrix multiplying dataframes (cannot apply matrices multiply )
```{r}
a.matrix <- matrix(c(35,8,10,4),nrow=2)
colnames(a.matrix) <- c("v1","v2")
a.matrix
a.matrix[,"v1"]  # Try a.matrix$v1 and see what happens
```


```{r}
a.data.frame <- data.frame(a.matrix,logicals=c(TRUE,FALSE))
a.data.frame
a.data.frame$v1
a.data.frame[,"v1"]
a.data.frame[1,]
a.data.frame[,1]
colMeans(a.data.frame)
```

### rbind
We can add rows or columns to an array or data-frame with `rbind()` and `cbind()`, but be careful about forced type conversions
```{r}
rbind(a.data.frame,list(v1=-3,v2=-5,logicals=TRUE))
rbind(a.data.frame,c(3,4,6))#6 is not a boolean variable, thus the last col becomes a numeric one
```


### composed by many vectors(different types)
thus when it comes to regression, multiple kinds of variables and binary variable can be easily used in the model.
### e.g. Eigenstuff
### class()
object oriented function